Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
quick caption edits

\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & distortion \\ \hline \hline
1 & $0.066081$ \\
10 & $0.045579$ \\
50 & $0.038302$ \\
100 & $0.035904$ \\
500 & $0.030841$ \\ \hline
\end{tabular}
\end{center}
\caption{\small{Experiment with the codebook size. We train on patterns
corresponding to $1$ bar resized to $4$ beats. 
The number of training samples is $50000$.
}}
\label{tab:cbsize}
\end{table}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.7\columnwidth]{freqs}
\end{center}
\caption{\small{
Frequency of use of the patterns in Figure \ref{fig:codes1} on the
artist20 dataset. 
There is $71832$ patterns in total in the dataset.
Note that all codes were initialized with a random
sample from the training set, some might not just be present in this
test set.
}}
\label{fig:freqs}
\end{figure}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & distortion \\ \hline \hline
1 & $0.066081$ \\
10 & $0.045579$ \\
50 & $0.038302$ \\
100 & $0.035904$ \\
500 & $0.030841$ \\ \hline
\end{tabular}
\end{center}
\caption{\small{Varying codebook size using $50,000$ training samples.
    We train on patterns corresponding to $1$ bar resized to $4$ beats.
  }}
\label{tab:cbsize}
\end{table}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.7\columnwidth]{freqs}
\end{center}
\caption{\small{ Usage frequency of the patterns in the codebook from
    Figure \ref{fig:codes1} on the artist20 dataset.  There are $71,832$
    patterns in total in the dataset.  Note that all codes were
    initialized with a random sample from the training set and might
    not be used in this test set.
    FIXME: so why not show usage in training data?  I think test.mat
    should contain this information.
  }}
\label{fig:freqs}
\end{figure}
